% start journal version
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% lyan 01/25/2013 (Elsevier format)
% lyan Friday, January 25, 2013 (add example)
% Tue Aug 28 2012, 09:55:36
% marek Sat Jul 14 13:24:51 PDT 2012
% marek Fri Jul 13 15:51:33 PDT 2012
% lyan Thu Jul 12 2012, 00:06:30
% lyan Wed Jul 04 2012, 22:29:33
%
% marek Fri Oct 26 01:59:39 PDT 2012


\documentclass[preprint,12pt]{elsarticle}

\usepackage{fullpage,amssymb,amsthm,caption,subcaption,enumerate,graphicx}
\usepackage[nosumlimits]{amsmath}
\usepackage[nothing]{algorithm}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage{array}

\floatname{algorithm}{Pseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\journal{Journal of Discrete Algorithms}
\input{macros.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}
  \title{LP-rounding Algorithms for the Fault-Tolerant\\
    Facility Placement Problem\tnoteref{t1}} \tnotetext[t1]{A
    preliminary version of this article appeared in Proc. CIAC 2013.}

\author{Li Yan\corref{cor1} and Marek Chrobak\fnref{fn1}}
\ead{\{lyan,marek\}@cs.ucr.edu}
\address{Department of Computer Science\\
 University of California at Riverside\\
Riverside, CA 92521, USA}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{Work supported by NSF grants CCF-0729071 and CCF-1217314.}
%\thispagestyle{empty}
\begin{abstract} 
  The Fault-Tolerant Facility Placement problem (FTFP) is a
  generalization of the classic Uncapacitated Facility
  Location Problem (UFL). In FTFP we are given a set of
  facility sites and a set of clients. Opening a facility at
  site $i$ costs $f_i$ and connecting client $j$ to a
  facility at site $i$ costs $d_{ij}$. We assume that the
  connection costs (distances) $d_{ij}$ satisfy the triangle
  inequality. Multiple facilities can be opened at any
  site. Each client $j$ has a demand $r_j$, which means that
  it needs to be connected to $r_j$ different facilities
  (some of which could be located on the same site). The
  goal is to minimize the sum of facility opening cost and
  connection cost.

  The main result of this paper is a $1.575$-approximation algorithm
  for FTFP, based on LP-rounding. The algorithm first reduces the
  demands to values polynomial in the number of sites. Then it uses a
  technique that we call adaptive partitioning, which partitions the
  instance by splitting clients into unit demands and creating a
  number of (not yet opened) facilities at each site. It also
  partitions the optimal fractional solution to produce a fractional
  solution for this new instance.  The partitioned fractional solution
  satisfies a number of properties that allow us to exploit existing
  LP-rounding methods for UFL to round our partitioned solution to an
  integral solution, preserving the approximation ratio.  In
  particular, our $1.575$-approximation algorithm is based on the
  ideas from the $1.575$-approximation algorithm for UFL by
  Byrka~\etal, with changes necessary to satisfy the fault-tolerance
  requirement.
\end{abstract}

\begin{keyword}
Facility Location \sep Approximation Algorithms
\end{keyword}

\end{frontmatter}

%\pagebreak
%\setcounter{page}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{intro.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LP ForMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{lpformulation.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% REDUCTION TO POLYNOMIAL DEMANDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{reduction.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ADAPTIVE PARTITION  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{partition.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% 3-APPROXIMATION ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{three_approx.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% 1.736-APPROXIMATION ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{ECHS.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Byrka 2010 1.575
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{EBGS.tex}

%%%%%%%%%%%%%%%%%%%%%%

\section{Final Comments}

In this paper we show a sequence of LP-rounding approximation algorithms
for FTFP, with the best algorithm achieving  ratio $1.575$. 
As we mentioned earlier, we believe that 
our techniques of demand reduction and adaptive partitioning are very flexible and
should be useful in extending other LP-rounding methods for UFL to obtain
matching bounds for FTFP.

One of the main open problems in this area is whether FTFL can be approximated with the
same ratio as UFL, and our work was partly motivated by this question. The techniques we
introduced are not directly applicable to FTFL, mainly because our partitioning
approach involves facility splitting that could result in several sibling demands being served
by facilities on the same site. Nonetheless, we hope that further refinements of 
our construction might get around this issue and
lead to new algorithms for FTFL with improved ratios.
\pagebreak

\bibliographystyle{elsarticle-num}
\bibliography{facility}

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\section{Proof of Lemma~\ref{lem: EBGS target connection cost}}
  Lemma~\ref{lem: EBGS target connection cost} provides a bound on the
  expected connection cost of a demand $\nu$ when none of
  $\wbarN(\nu)$ opens by the algorithm. The formal proof is very
  similar to that in \cite{ByrkaA10}, and we sketch the main steps
  here for completeness.

  Let $K_1 = \wbarclsnb(\kappa) \setminus \wbarN(\nu), K_2 =
  \wbarclsnb(\kappa) \cap \wbarclsnb(\nu)$ and $K_3 =
  \wbarclsnb(\kappa) \cap \wbarfarnb(\nu)$, then we shall show that
  $D(K_1, \nu) \leq \clsdist(\kappa)+\clsmax(\kappa) + 
  \fardist(\nu)$, which implies $D(K_1, \nu) \leq \clsdist(\nu) +
  \clsmax(\nu) + \fardist(\nu)$ due to
  (PD'.\ref{PD1:assign:cost}). Recall that $D(A,\nu)
  \stackrel{\mathrm{def}}{=} \sum_{\mu\in A} d_{\mu\nu}\bary_{\mu}$ is
  the average distance of facilities in set $A$ to demand $\nu$.

  We can dismiss a few simple cases: If $D(K_1, \kappa) \leq
  \clsdist(\kappa)$, then we can use any facility $\mu \in K_2$ to
  show that $D(K_1,\nu) \leq D(K_1, \kappa) + d_{\mu\kappa} +
  d_{\mu\nu} \leq \clsdist(\kappa) + \clsmax(\kappa) + \fardist(\nu)$
  because $d_{\mu\kappa} \leq \clsmax(\kappa)$ and $d_{\mu\nu} \leq
  \clsmax(\nu) \leq \fardist(\nu)$, and we are done. So we can assume
  $D(K_1, \kappa) > \clsdist(\kappa)$. Our second assumption is that
  every $\mu \in K_2$ has $d_{\mu\kappa} > \clsdist(\kappa)$, for
  otherwise we can use $\clsmax(\kappa)$ to bound $D(K_1, \kappa)$ and
  there exists a facility $\mu\in K_2$ such that $d_{\mu\kappa} \leq
  \clsdist(\kappa)$. Since $\mu\in K_2$, we infer that $d_{\mu\nu}
  \leq \clsmax(\nu) \leq \fardist(\nu)$, and we are done as well.

  Given the two assumptions we can now assume that $K_3$ is not empty
  and there exists some finite number $\delta > 0$ such that $D(K_3,
  \kappa) = \clsdist(\kappa) - \delta$. This in turn implies $D(K_3,
  \nu) \geq \fardist(\nu) + \delta$, or we will be done. Because $K_3$
  is a subset of $\wbarfarnb(\nu)$, this gives us a bound on
  $D(\wbarfarnb(\nu) \setminus K_3, \nu)$, which in turn, is an upper
  bound on $\clsmax(\nu)$. Let $\hat{y} = \gamma \sum_{\mu\in K_3}
  \bary_{\mu}$, using the fact that $\fardist(\nu) = D(K_3,\nu)\;
  \hat{y}/(\gamma-1) + D(\wbarfarnb(\nu)\setminus K_3)\;
  (\gamma-1-\hat{y})/(\gamma-1)$, we are able to show that
  \begin{equation*}
    \clsmax(\nu) \leq D(\wbarfarnb(\nu) \setminus K_3, \nu) \leq \fardist(\nu) -
    \hat{y}\delta/(\gamma-1-\hat{y}) \leq \fardist(\nu) -
    \hat{y}\delta/(1-\hat{y}),
  \end{equation*}
  since $\gamma \leq 2$ (we pick $\gamma=1.575$ in the end). On the
  other hand, since $\wbarclsnb(\kappa) = K_1 \cup K_2 \cup K_3$, we
  have $\clsdist(\kappa) = (1-\hat{y})\; D(K_1\cup K_2, \kappa) +
  \hat{y}\; D(K_3, \kappa)$, which implies that
  \begin{equation*}
    D(K_1 \cup K_2, \kappa) = \clsdist(\kappa) + \hat{y}\delta/(1-\hat{y}).
  \end{equation*}

  Now we are essentially done. If there exists some $\mu \in K_2$ such
  that $d_{\mu\kappa} \leq \clsdist(\kappa) +
  \hat{y}\delta/(1-\hat{y})$, then we have
  \begin{align*}
    D(K_1, \nu) &\leq D(K_1, \kappa) + d_{\mu\kappa} + d_{\mu\nu} \\
    &\leq \clsmax(\kappa) + \clsdist(\kappa) +
    \hat{y}\delta/(1-\hat{y})
    + \clsmax(\nu)\\
    &\leq \clsmax(\kappa) + \clsdist(\kappa) + \fardist(\nu)
  \end{align*}
  Otherwise we must have $D(K_1, \kappa) \leq \clsdist(\kappa) +
  \hat{y}\delta/(1-\hat{y})$. It follows that
  \begin{align*}
    D(K_1, \nu) &\leq D(K_1, \kappa) + d_{\mu\kappa} + d_{\mu\nu} \\
    &\leq \clsdist(\kappa) + \hat{y}\delta/(1-\hat{y}) +
    \clsmax(\kappa)
    + \clsmax(\nu)\\
    &\leq \clsmax(\kappa) + \clsdist(\kappa) + \fardist(\nu).
  \end{align*}

  This concludes the proof of Lemma~\ref{lem: EBGS target connection
    cost}, and we have the desired bound on the expected distance when
  the algorithm connnects a demand $\nu$ indirectly to its target
  facility, that is, the facility opened by the primary demand that
  $\nu$ was assigned.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Proof of an Inequality for Analysis of Algorithm~{\ECHS}}

In the $1+2/e=1.736$-approximation in Section~\ref{sec: 1.736-approximation}
we need to show the following inequality
%
\begin{equation}
  \label{eq:dist}
\sum_{u=1}^l d_uy_u\prod_{s=1}^{u-1}(1-y_s)
  \;\leq\;  \Big(1 - \prod_{s=1}^l (1-y_s)\Big) \cdot \sum_{u=1}^l d_u y_u
\end{equation}
%
for $d_1\leq d_2 \leq \ldots \leq d_l$ and $\sum_{s=1}^l y_s = 1, y_s \geq 0$.

In this section we give a new proof of this inequality, much
simpler than the existing proof in \cite{ChudakS04}, and also simpler than
the argument by Sviridenko~\cite{Svi02}.  
We derive this inequality from the following generalized version of the Chebyshev Sum
Inequality:
%
\begin{equation}
  \label{eq:cheby}
  \sum_{i} p_i \sum_j p_j a_j b_j \leq \sum_i p_i a_i \sum_j p_j b_j,
\end{equation}
%
where each summation below runs from $1$ to $l$ and the sequences 
$(a_i)$, $(b_i)$ and $(p_i)$ satisfy the following conditions:
$p_i\geq 0, a_i \geq 0, b_i \geq 0$ for all $i$, $a_1\leq a_2 \leq
\ldots \leq a_l$, and $b_1 \geq b_2 \geq \ldots \geq b_l$.

Given inequality (\ref{eq:cheby}), we can obtain our inequality
(\ref{eq:dist}) by simple substitution
%
\begin{equation*}
  p_i \leftarrow y_i, a_i \leftarrow d_i, b_i \leftarrow
  \Pi_{s=1}^{i-1} (1-y_s).
\end{equation*}

For the sake of completeness, we include the proof of inequality (\ref{eq:cheby}), 
due to Hardy, Littlewood and Polya~\cite{HardyLP88}. The idea is to evaluate the 
following sum:
%
\begin{align*}
  S &= \sum_i p_i \sum_j p_j a_j b_j - \sum_i p_i a_i \sum_j p_j b_j
	\\
  & = \sum_i \sum_j p_i p_j a_j b_j - \sum_i \sum_j p_i a_i p_j b_j
	\\
  & = \sum_j \sum_i p_j p_i a_i b_i - \sum_j \sum _i p_j a_j p_i b_i
	\\
	&= \half \cdot \sum_i \sum_j (p_i p_j a_j b_j - p_i a_i p_j b_j + p_j p_i a_i
  							b_i - p_j a_j p_i b_i)
\\
  &= \half \cdot \sum_i \sum_j p_i p_j (a_i - a_j)(b_i - b_j) \leq 0.
\end{align*}
The last inequality holds because $(a_i-a_j)(b_i-b_j) \leq 0$, since the sequences
$(a_i)$ and $(b_i)$ are ordered oppositely.

\end{document}

% marek Tue Jul  3 10:21:05 PDT 2012
% marek Sun Jul  1 14:57:39 PDT 2012
% lyan Sat Jun 30 2012, 22:01:27
% marek Sat Jun 30 10:08:59 PDT 2012
% lyan Fri Jun 29 19:54:18 PDT 2012
% marek Thu Jun 28 09:21:14 PDT 2012
% lyan Thu Jun 28 00:11:28 PDT 2012
% marek Wed Jun 27 11:24:07 PDT 2012
% lyan Wed Jun 27 2012, 10:08:21
% marek Tue Jun 26 14:48:45 PDT 2012
% lyan Mon Jun 25 2012, 22:23:13
% marek Sun Jun 24 16:46:23 PDT 2012
% marek Wed Jun 20 04:42:40 PDT 2012
% lyan, Sun Jun 17 2012, 09:49:22
% marek Sat Apr  7 16:42:21 PDT 2012
% marek Thu Apr  5 11:39:58 PDT 2012
% marek Wed Apr  4 11:28:20 PDT 2012
% lyan, 04/01/12 10:20 PM
% lyan, Mon Mar 26 2012, 09:10:54
% lyan, Tue Mar 20 2012, 23:28:17
% lyan, 03/18/12 12:28 PM
% marek Sat Mar 17 13:42:32 PDT 2012
% marek, Wed Mar  7 21:28:24 PST 2012
% marek Mon Mar 12 12:08:25 PDT 2012
