\documentclass[11pt]{article}

\title{On primal-dual and dual-fitting of the FTFP problem}
\author{UCR theory lab}
\usepackage{fullpage, amsmath}

\begin{document}
\maketitle

\section{A Possible Explanation of the Difficulty in Dual-fitting Analysis}
For FTFP, the greedy algorithm that repeatedly picks the best star
until all clients have all demands satisfied can be implemented in
polynomial time and in Section~\ref{sec:upp} we show that this
algorithm is $H_n$-approximation where $n=|\mathcal C|$ is the number
of clients. Since the same greedy algorithm is shown to have constant
approximation ratio for UFL, a natural question to ask is whether
greedy can be shown to have $O(1)$ approximation ratio. Here we give
an argument that hints a negative answer.

We assume the greedy algorithm is analyzed using the dual-fitting
technique, which associates with client $j$ with a number $\alpha_j$
and show that by shrinking the dual solution by some factor $\gamma$,
all dual constraints are satisfied, that is $\sum_{j\in \mathcal C}
(\alpha_j/\gamma - d_{ij})_+ \leq f_i$ for all $i\in \mathcal F$. Then
$\gamma$ is an upper bound on the approximation ratio.

In the greedy algorithm, a star with minimum average cost is picked at
each iteration and each member client of that star then gets one more
connection. It is not specified by the algorithm how we distribute the
cost of $f_i$ into member clients, which is part of the
analysis. Nonetheless we assume that the cost of $f_i$ is distributed
among members only, and not to clients outside this star. We call this
\emph{local charging} assumption. Our second assumption is that the
proposed dual variable value $\alpha_j$, is taken as the average of
individual $\alpha_j^l$ for each of the $l^{th}$ demand of client $j$,
with $l=1,\ldots,r_j$. Suppose the $l^{th}$ demand of $j$ is satisfied
while $j$ is in a star with facility $i$, then $\alpha_j^l = d_{ij} +
f_j^l$, where $f_j^l$ is the portion of $f_i$ attributed to $j$ in the
analysis.

Our example has one site and $k$ groups of clients. Opening one facility
at that site costs $f_1$. The first group has $n_1$ clients each with
demand $r_1$, all at distance $d_1 = 0$ from $f_1$. The other groups
are listed below:
\begin{align*}
  &d_1 = 0\\
  &d_2 = \frac{f_1}{n_1}\\
  &d_3 = f_1/n_2 + d_2 = f_1/n_2 + f_1/n_1 = f_1 (\frac{1}{n_2} + \frac{1}{n_1})\\
  &\ldots\\
  &d_k = f_1/n_{k-1} + d_{k-1} = f_1 (\frac{1}{n_{k-1}} + \ldots + \frac{1}{n_1})\\
\end{align*}
For the numbers, we need $r_1 \ll r_2 \ll \ldots \ll r_k$, and $n_1 =
u^k, n_2 = u^{k-1}, \ldots, n_k = u$ for some number $u$ (actually we
take $u=k$ currently, this choice may not be the best possible).

Now the greedy execution goes like this: First star (with $r_1$
replica) is $(f_1, n_1)$.  Second star (with $r_2$ replica) is $(f_1,
n_2)$. Notice that $r_2 \gg r_1$, and we also have some stars with a
zero-cost $f_1$ which satisfies some demand of $n_2$ group. After that
the $n_2$ group clients each has residual demand $r_2 - r_1 =
r_2$. The process repeats until the $k^{th}$ group finishes with $r_k$
new facilities.

According to our local charging assumption, we have $\alpha_1 = f_1$
which is the total dual value of group $n_1$, regardless how the
analysis would distribute within that group. Similarly $\alpha_2 = f_1
+ n_2 d_2$, and so on. Substituing in the numbers, we have

\begin{align*}
  &\alpha_1 = f_1\\
  &\alpha_2 = f_1 + n_2 d_2 = f_1 + f_1/n_1 n_2 = f_1 (1 + n_2 /
  n_1)\\
  &\alpha_3 = f_1 + n_3 d_3 = f_1 + f_1 (\frac{1}{n_2} +
  \frac{1}{n_1}) n_3 = f_1 (1 + \frac{n_3}{n_2} + \frac{n_3}{n_1})\\
  &\ldots\\
  &\alpha_k = f_1 + n_k d_k = f_1 + f_1 n_k (\frac{1}{n_{k-1}} + \ldots
  \frac{1}{n_1})\\
\end{align*}
Notice that $r_1 \ll r_2 \ll \ldots \ll r_k$ implies $\alpha_j$ is
decided by the max among $\alpha_j^l$.

Now back to the dual constraint, it requires that the shrinking factor
$\gamma$ needs to satisfy the following inequality:
\begin{equation}
  \frac{\alpha_1}{\gamma} - d_1 + \frac{\alpha_2}{\gamma} - d_2 +
  \ldots + \frac{\alpha_k}{\gamma} - d_k \leq f_1.
\end{equation}
Substitute in the $\alpha_j$ values derived above, we have
\begin{align*}
  \gamma &\geq (\sum_{j=1}^k \alpha_j) / (f_1 + \sum_{j=1}^k d_j)\\
  &\geq \frac{f_1 + n_1 d_1 + f_1 + n_2 d_2 + f_1 + n_3 d_3 + \ldots +
    f_1 + n_k
    d_k}{f_1 + n_1 d_1 + n_2 d_2 + \ldots + n_k d_k}\\
  &= 1 + (k-1)f_1 / (f_1 + n_1 d_1 + n_2 d_2 + \ldots + n_k d_k)\\
  &= 1 + (k-1)f_1 / \left(f_1 + n_2 f_1 / n_1 + \ldots + n_k f_1
    (\frac{1}{n_{k-1}} + \frac{1}{n_{k-2}} + \ldots +
    \frac{1}{n_1})\right)\\
  &= 1 + (k-1) / \left(1 + n_2 / n_1 + \ldots + n_k
    (\frac{1}{n_{k-1}} + \frac{1}{n_{k-2}} + \ldots +
    \frac{1}{n_1})\right)\\
  &= 1 + (k-1) / \left(1 + 1/u + \ldots + (\frac{1}{u} + \ldots +
    \frac{1}{u^{k-1}})\right)\\
  &= 1 + (k-1) / \left(1 + k/u + (k-1)/u^2 + \ldots +
    1/u^{k-1}\right)\\
  &\geq 1 + (k-1) / \left(1 + k/u + k/u^2 + \ldots +
    k/u^{k-1}\right)\\
  &= 1 + (k-1) / \left(1 + 1 + 1/k + \ldots + 1/k^{k-2}\right)\\
  &\approx k/2\\
\end{align*}
So for $k$ groups we can force a shrinking factor $\gamma$ as big as
$k/2$. Recall that we have greedy being no more than
$H_n$-approximation. Is that a contradiction? No, because we have
$n=k^k + k^{k-1} + \ldots + k = k^k$, so $k = O(\log n / \log\log
n)$. Therefore, the example shows that dual fitting with local
charging cannot hope to get $O(\log n / \log\log n)$ ratio or better.

Notice this example is similar in spirit to the $\Omega(\log n/
\log\log n)$ example for Hochbaum's algorithm for UFL, consructed by
Mahdian et al.

\section{$H_n$-approximation of Star-greedy on FTFP}
\label{sec:upp}
In this section we show that the star-greedy algorithm which
repeatedly picking the best star (the one with minimum
average cost) gives an approximation ratio of $H_n = \ln(n)$
where $n=|\mathcal{C}|$ is the number of clients.

When we run the star-greedy algorithm, for every client $j$,
we associate each demand of $j$ with a number $\alpha_j^l$,
which is the average cost of the star when $l^{th}$ demand
of $j$ is connected. Now we let $\alpha_j = \alpha_j^{r_j}$,
that is, take $\alpha_j$ to be the finishing $\alpha_j^l$,
and order clients by increasing $\alpha_j$. That is,
\begin{equation*}
  \alpha_1 \leq \alpha_2 \leq \ldots \leq \alpha_n
\end{equation*}

Due to the algorithm, for every $j=1,\ldots,n$, we have
\begin{equation*}
  \sum_{l=j}^n (\alpha_j - d_{il})_+ \leq f_i
\end{equation*}
for every facility $i$.  The reason is that, when the last
demand of $j$ is connected, all clients $j+1,\ldots,n$ are
still active so their total contribution cannot exceed
$f_i$.

Now we take a closer look at the numbers $\{\alpha_j\}$. We
know that the algorithm's total cost is exactly
$\sum_{j=1}^n \sum_{l=1}^{r_j} \alpha_j^l$, which is no more
than $\sum_{j=1}^n r_j \alpha_j$ since we take $\alpha_j$ to
be $\alpha_j^{r_j}$. Now if we can show that $\sum_{j=1}^n
r_j \alpha_j$ is no more than $\gamma \cdot \textrm{OPT}$,
where $\textrm{OPT}$ is the cost of an integral optimal
solution to the given FTFP instance, then we claim our
algorithm returns an integral solution within a factor of
$\gamma$.

We show that $\sum_{j=1}^n r_j \alpha_j$ is within a factor
of $\gamma$ from $\textrm{OPT}$ by showing that
$\{\alpha_j/\gamma\}$ is a feasible dual solution to the
following program, which is the dual program of the primal
LP for FTFP.
\begin{align*}
  \max\; &\sum_j r_j\alpha_j\\
  \textrm{subject to: }& \sum_{j=1}^n (\alpha_j - d_{ij})_+
  \leq f_i \textrm{ for every facility i}\\
\end{align*}

To find the minimum $\gamma$ that would shrink
$\{\alpha_j\}$ to a feasible dual solution, we need to find
a worst case instance to maximize $\gamma$, also it is clear
that the worst case instance must contain a star whose
feasibility requirement would achieves the value of
$\gamma$, and this star would be the worst star in that
instance.

As a first step we can drop the $\max\{0, \cdot\}$, because
we can always find a new star by dropping those $j$ with
$\alpha_j - d_{ij}$ term negative, and that new star would
still be a worst case star. Suppose a worst case star has
$k$ clients, and is with facility $i$, then we have
\begin{equation*}
  \sum_{j=1}^k \alpha_j - d_{ij} \leq f_i
\end{equation*}
Here we rename clients in the new star to be $1,\ldots,k$,
although among them, they are still ordered by their
$\alpha_j$.

Now our goal is to find a supremum of the following program:
\begin{align*}
  \max\; & \frac{\sum_{j=1}^k \alpha_j}{f_i + \sum_{j=1}^k d_{ij}}\\
  \textrm{subject to: } & \sum_{l=j}^k (\alpha_l -
  d_{il})_+\leq f_i \textrm{ for } j=1,\ldots,n\\
\end{align*}

Since we are dealing with a particular star, we can abstract
away $i$, to obtain the following program:
\begin{align}
  \label{eq:star}
  \max\; & \frac{\sum_{j=1}^k \alpha_j}{f + \sum_{j=1}^k
    d_j}\\ \notag
  \textrm{subject to: } & \sum_{l=j}^k (\alpha_j - d_{l})_+
  \leq f \textrm{ for } j=1,\ldots,n\\ \notag
\end{align}

Now we claim we can drop the $\max\{0, \cdot\}$ operator
because this would relax the constraint in (\ref{eq:star})
and can only make objective value larger (since we are
maximizing), so the real optimal is upper bounded by the
relaxed optimal. This allows us to work on
\begin{align}
  \label{eq:frlp}
  \max\; & \frac{\sum_{j=1}^k \alpha_j}{f + \sum_{j=1}^k
    d_j}\\ \notag
  \textrm{subject to: } & \sum_{l=j}^k (\alpha_j - d_{l})
  \leq f \textrm{ for } j=1,\ldots,n\\ \notag
\end{align}

For each $j=1,\ldots,n$, the constraint above simply can be
rewritten as
\begin{equation}
  (k-j+1) \alpha_j \leq f + \sum_{l=j}^k d_l \leq f +
  \sum_{l=1}^k d_l.
\end{equation}
The first inequality is a rewrite of the constraint in
(\ref{eq:frlp}) and the second is straightforward.

Therefore we have $\alpha_j \leq (1/(k-j+1)) (f +
\sum_{j=1}^k d_j)$, and it easily follows that
\begin{equation}
  \sum_{j=1}^n \alpha_j \leq (1/k + 1/(k-1) + \ldots + 1) =
  H_k \leq H_n = \ln(n)
\end{equation}

\section{Dual-fitting Analysis on FTFP}
\label{sec:dual2}
This section gives a simple example that the dual-fitting analysis of
a greedy algorithm which repeatedly picking the most cost-effective
star (the star with minimum average cost) is unlikely to give the same
ratio as that for the UFL problem.

The example consists of $1$ facility with cost $f_1 = n$, and $n$
clients with demands $r_1=r_2=\ldots=r_{n-1} = 1$ and $r_n = n$. All
$d_{ij} = 0$. Now running the star-greedy algorithm, we will first
pick a star with all $n$ clients and we open $1$ copy of facility
$f_1$. We then have only client $n$ with residual demand $r_n' = n-1$,
and we have no other option but to open facility $f_1$ for another
$n-1$ copies.

Now the dual-fitting based analysis will associate each demand with a
dual variable $\alpha_j^1, \ldots, \alpha_j^{r_j}$ and the proposed
dual solution is $\bar\alpha_j = \sum_{l=1}^{r_j} \alpha_j^{l} / r_j$
and try to find a minimum $\gamma$ such that $\{\bar\alpha_j/\gamma\}$
is a feasible dual, that is
\begin{equation}
  \sum_{j=1}^n (\bar\alpha_j/\gamma - d_{1j})_+ \leq f_1 = n
\end{equation}
which is
\begin{equation}
  \sum_{j=1}^n \bar\alpha_j/\gamma  \leq n
\end{equation}
since all $d_{ij}=0$ and $f_1 = n$.

From the greedy algorithm, we have $\alpha_j^1 = 1$ for
$j=1,\ldots,n$, and $\alpha_n^l = n$ for $l=2,\ldots,n$. Therefore
$\bar\alpha_j = 1$ for $j=1,\ldots,n-1$ and $\bar\alpha_n =
(1+(n-1)n)/n = n-1$. The shrinking factor $\gamma$ we seek thus
satisfies
\begin{equation}
  \sum_{j=1}^{n-1} (\bar\alpha_j/\gamma - 0)_+ + (\bar\alpha_n/\gamma -0)_+
  \leq f_1 = n,
\end{equation}
which is
\begin{equation}
  (n-1)(1/\gamma)  + (n/\gamma) \leq n
\end{equation}
Simple algebra will show that $\gamma$ can be made arbitrarily close
to $2$ when $n$ is large. On the other hand we know that the same
greedy algorithm with dual-fitting analysis gives a ratio of $1.81$
for the UFL problem where all $r_j=1$.

This example does not actually rule out the possibility to prove a
constant ratio of the star-greedy algorithm on FTFP. In fact greedy
gets exactly the same solution as the optimal integral solution for
this example. All it says is that the dual-fitting analysis on greedy
algorithm, when applied to the FTFP or FTFL problem, cannot possibly
give a ratio much better than $2$. And this partly explains why
generalizing primal-dual or dual-fitting algorithms from UFL to
fault-tolerant problems like FTFL or FTFP is not successful when
$r_j$'s are not equal, that is demands are not uniform. Intuitively
there seems to be some issue fundamental to the dual-fitting approach
as the proposed dual solution $\bar\alpha_j$'s can be very different
between each other so shrinking all of them by a common factor
$\gamma$ might not give a strong upper bound on the approximation
ratio. It is also quite possible that the example may be strengthened
to show that dual-fitting cannot achieve a worse yet ratio.

\section{Dual-fitting Analysis can be $H_n$ on FTFP}
This section extends the idea in Section~\ref{sec:dual2} to show that
dual-fitting based analysis on greedy algorithm can be off by a factor
as large as $H_n = \ln(n)$. This complements the $\ln(n)$ upper bound
shown in Section~\ref{sec:upp}.

The example has one facility with $f_1 = 1$, all $d_{ij}=0$. There are
$n$ clients with demands $r_1, r_2, \ldots, r_n$ with $r1 \ll r_2 \ll
\ldots \ll r_n$. Now following the idea in Section~\ref{sec:dual2}, we
shall have the proposed dual variable with value $\alpha_1=1/n,
\alpha_2 = 1/(n-1), \alpha_3 = 1/(n-2), \ldots, \alpha_n = 1$. We take
the $\alpha_j$ value to be the average of the cost of individual
demand of a client, which is $\alpha_j^l$, so that the algorithm's
cost is equal to $\sum_{j} r_j\alpha_j$, since the algorithm's cost is
equal to $\sum_{j=1}^n \sum_{l=1}^{r_j} \alpha_j^l$ by definition. Now
we need a number $\gamma$ such that $\{\alpha_j/\gamma\}$ form a
feasible dual solution, that is, we need $\sum_{l=1}^n \alpha_j \leq
f_1 = 1$. It is easily seen that $\gamma$ needs to be at least $H_n =
\ln(n)$

\section{Star-Greedy and Dual-fitting on FTFL}
In this section we attempt to carry the claims and arguments developed
in earlier sections for FTFP to apply to FTFL, a better known
problem.

Recall in FTFL, we are given a set $\mathcal F$ facilities and a set of
$\mathcal C$ of clients, with each client $j$ having demand $r_j$,
meaning it needs to be connected to $r_j$ different facilities. Each
facility $i$ can be opened once with cost $f_i$. We are also given
$d_{ij}$ satisfying the triangle inequality. The main difference
between FTFL and FTFP is that FTFP allows an arbitrary number of
facilities to be opened on the same site $i$, each paying $f_i$. This
results in an extra constraint in the FTFL LP formulation.

\begin{align*}
  \text{minimize }& \sum_{i\in\mathcal{F}} f_i y_i +
  \sum_{i\in\mathcal{F}, j\in\mathcal{C}} d_{ij} x_{ij}\\
  \text{subject to: }& y_i \geq x_{ij}\\
  &\sum_{i\in\mathcal{F}} x_{ij} \geq r_j\\
  &y_i \leq 1\\
\end{align*}
and the dual program is
\begin{align}
  \label{eq:ftfl_dual}
  \text{maximize }& \sum_{j\in\mathcal{C}} r_j \alpha_j -
  \sum_{i\in\mathcal{F}} z_i\\ \notag
  \text{subject to: }& \sum_{\beta_{ij}} \leq f_i + z_i\\ \notag
  & \alpha_j - \beta_{ij} \leq d_{ij}\\ \notag
\end{align}

Now we use the same algorithm as before by greedily picking the star
with minimum average cost until all clients have been connected to
$r_j$ different facilities. This will again give us a sequence of
$\alpha_j^l$ numbers associated with each connection of a client
$j$. We could still order clients by $\alpha_j^{r_j}$, that is, their
last $\alpha_j$ value, or the average cost of the star that a client
makes its last connection.

Now we set the dual solution as $\alpha_j = {\alpha_j^{r_j}}$ and $z_i
= 0$. Then the objective of this dual solution is an upper bound on
the algorithm's cost, which is $\sum_{j\in\mathcal{C}}\sum_{l=1}^{r_j}
\alpha_j^l$. We then show that $(\alpha_j/H_n, z_i/H_n)$ is a feasible
dual to (\ref{eq:ftfl_dual}), thereby establishing the approximation
ratio being $H_n$. The proof is very similar to that in
Section~\ref{sec:upp}.

On the other hand, the example in Section~\ref{sec:dual2} can also be
used for FTFL, thus showing that greedy algorithm analyzed using
dual-fitting cannot give a ratio better than $2$. Recall that for UFL
where all $r_j=1$, the greedy algorithm was shown to have a ratio of
$1.81$ using dual-fitting analysis.

The result compares favorably to the first result on FTFL, in which
Jain and Vazirani showed that FTFL can be approximated to a ratio of
$3H_n$ using a generalized version of the JV algorithm. The result of
$H_n$ improves it by a factor of $3$.

\section{$O((\log R/\log\log R)^2) approximation$}
It appears that FTFP can be approximated to ratio $O((\log R / \log\log
R)^2)$ quite easily, by taking advantage that an instance with $R =
\max_j r_j$ can be approximates to ratio no more than $R$ easily.

The idea is to pick $k$ such that $k^k = R$ where $R = \max_j
r_j$. Now we group clients by their $r_j$ such that $[1,k), [k,k^2),
\ldots, [k^{k-1}, k^k]$ so we have $k$ groups. Solve each group using
any primal-dual algorithm gives a partial solution with at most $k$
times opt of that partial instance. Now combine the partial solutions
we obtain one integral solution. Notice that each optimal integral
solution to the original instance can have each of its facility
duplicated $k$ times and then decompose into feasible integral
solutions to each of the sub-instances. This shows that the combined
solution has cost no more than $k$ times overall opt. And in solving
each sub-instance, we find a solution no more than $k$ times the opt
for that sub-instances. Overall we have a solution with ratio $k*k =
k^2$, which is better than $\log R$.

\section{Future Directions}
It seems the greedy algorithm is likely to give a constant ratio,
although two things have to happen:
\begin{itemize}
\item We need to use an analysis different from dual-fitting.
\item We have to use the triangle inequality somewhere, without that
  the approximation ratio cannot be better than $H_n$ and examples
  from non-metric UFL already shows a lower bound of $H_n$ in approximation.
\end{itemize}

\section{On $O(1)$-approximation on Greedy Algorithm}
Now we seek to show a ratio of $O(1)$ for the greedy algorithm that
repeatedly picks the best star until all clients are fully-connected.

The special instance we consider is the example that we use to show
greedy using dual-fitting analysis can be a factor of $H_n$ away from
being dual-feasible. In this example, there is one site with $f_i=1$
and all clients are co-located at the same point of that site, that is
$d_{ij}=0$ for all $i,j$. There are $n$ clients and their demands are
$r_1 \leq r_2 \leq \ldots \leq r_n$. Then the greedy algorithm will
first create $r_1$ facilities and each of the $n$ clients will make
$r_1$ connections to them. The next round will create another $r_2 -
r_1$ facilities and clients $2$ to $n$ will make that many connections
and so on, until the $n^{th}$ round client $n$ will create $r_n -
r_{n-1}$ new facilities and connect to them.

The algorithm only concerns which star to pick and how to make
connections, it does not specify how to share cost among participating
clients of a star, and that is part of the analysis. We now look for a
charging scheme that would resolve the $H_n$ shrinking factor and keep
it to a constant. The scheme at a high level is to group clients with
the same $r_j$ and then distribute facility cost proportional to $r_j$
to each group. Within a group we distribute cost to clients
evenly. For the convenience of analysis, we actually round each $r_j$
up to the nearest power of $2$, that is $r_j'=2^k$ for some $k$ such
that $2^{k-1} < r_j \leq 2^k$, and we will work on $r_j'$. This will
at most double the total cost.

According to our scheme, w.l.o.g. we can assume $r_j'$ are distinct
and they are all powers of 2. Let $R_k = \sum_{j=k}^n r_j'$, then
client $1$ has its share being $r_1'/R_1$, it has $r_1'$ demands to
satisfy and therefore its $\alpha_1 = r_1'/R_1$. Similarly for demand
$2$, we have $\alpha_2 = 1/r_2' (r_1'\cdot r_2'/R_1 +
(r_2'-'r_1')\cdot r_2'/R_2) = r_1'/R_1 + (r_2'-r_1')/R_2$. If we sum
all $\alpha_j$ for $j=1,\ldots,n$, we obtain
\begin{equation}
S_n = n\cdot r_1'/R_1 + (n-1) (r_2'-r_1')/R_2 + \ldots + (r_n' -
r_{n-1}') / R_n
\end{equation}

It is easy to see that
\begin{align*}
S_n &= n\cdot r_1'/R_1 + (n-1) (r_2'-r_1')/R_2 + \ldots + (r_n' -
r_{n-1}') / R_n\\
&\leq n\cdot r_1'/R_1 + (n-1) r_2' / R_2 + \ldots + r_n' / R_n\\
&\leq n\cdot r_1'/r_n' + (n-1) r_2' / r_n' + \ldots + r_n' / r_n'\\
&\leq n/2^n + (n-1)/2^{n-1} + \ldots + 1\\
&\leq 2 = O(1)\\
\end{align*}

\end{document}
