% start journal version
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tue Aug 28 2012, 09:55:36
% marek Sat Jul 14 13:24:51 PDT 2012
% marek Fri Jul 13 15:51:33 PDT 2012
% lyan Thu Jul 12 2012, 00:06:30
% lyan Wed Jul 04 2012, 22:29:33
%
% marek Fri Oct 26 01:59:39 PDT 2012



\documentclass[11pt]{article}

\usepackage{fullpage,amssymb,amsthm,enumerate}
\usepackage[nosumlimits]{amsmath}
\usepackage[nothing]{algorithm}
\usepackage{algorithmicx}
%\usepackage[noend]{algorithmic}
\usepackage[noend]{algpseudocode}
%\usepackage[firstinits=true]{biblatex}

%\algsetup{indent=2em}
\floatname{algorithm}{Pseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\input{macros.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{LP-rounding Algorithms for the Fault-Tolerant\\
 		Facility Placement Problem}

\author{Li Yan and Marek Chrobak\\
  Department of Computer Science\\
 University of California at Riverside}

\date{}

\begin{document}
\maketitle

\thispagestyle{empty}
\begin{abstract} 
  The Fault-Tolerant Facility Placement problem (FTFP) is a
  generalization of the classic Uncapacitated Facility
  Location Problem (UFL). In FTFP we are given a set of
  facility sites and a set of clients. Opening a facility at
  site $i$ costs $f_i$ and connecting client $j$ to a
  facility at site $i$ costs $d_{ij}$. We assume that the
  connection costs (distances) $d_{ij}$ satisfy the triangle
  inequality. Multiple facilities can be opened at any
  site. Each client $j$ has a demand $r_j$, which means that
  it needs to be connected to $r_j$ different facilities
  (some of which could be located on the same site). The
  goal is to minimize the sum of facility opening cost and
  connection cost.

  The main result of this paper is a $1.575$-approximation
  algorithm for FTFP, based on LP-rounding. The algorithm
  first reduces the demands to values polynomial in the
  number of sites. Then it uses a technique that we
  call adaptive partitioning, which partitions the instance
  by splitting clients into unit demands and creating a
  number of (not yet opened) facilities at each site. It
  also partitions the optimal fractional solution to produce
  a fractional solution for this new instance.  The
  partitioned instance satisfies a number of properties that
  allow us to exploit existing LP-rounding methods for UFL to
  round our partitioned solution to an integral
  solution, preserving the approximation ratio.  In
  particular, our $1.575$-approximation algorithm is based
  on the ideas from the $1.575$-approximation algorithm for
  UFL by Byrka~\etal, with changes necessary to satisfy
  the fault-tolerance requirement.
\end{abstract}

\pagebreak
\setcounter{page}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{intro.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LP ForMULATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{lpformulation.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% REDUCTION TO POLYNOMIAL DEMANDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{reduction.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ADAPTIVE PARTITION  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{partition.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% 3-APPROXIMATION ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{three_approx.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% 1.736-APPROXIMATION ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{ECHU.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Byrka 2010 1.575
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{EBGS.tex}

%%%%%%%%%%%%%%%%%%%%%%
\section{Discussions}

In this paper we show a sequence of LP-rounding approximation algorithms
for FTFP, with the best algorithm achieving  ratio $1.575$. The two techniques we introduced,
namely the demand reduction and adaptive partitioning, are very flexible. Should any new
LP-rounding algorithms be discovered for UFL, we believe that with our approach they can be
adapted to FTFP as well, preserving the approximation ratio. In fact, by randomizing the
scaling parameter $\gamma$ from Section~\ref{sec: 1.575-approximation},
following the approach by Li~\cite{Li11}, we
could further improve the ratio to below $1.575$. This is not enough, however, to
match the $1.488$ bound for UFL in~\cite{Li11}, because matching this bound
also requires appropriately extending dual-fitting algorithms~\cite{MahdianYZ06}
to FTFP, which we have so far been unable to do.

One of the main open problems in this area is whether FTFL can be approximated with the
same ratio as UFL, and our work was partly motivated by this question. The techniques we
introduced are not directly applicable to FTFL, mainly because our partitioning
approach involves facility splitting that could result in several sibling demands being served
by facilities on the same site. Nonetheless, we hope that further refinements of 
our construction might get around this issue and
lead to new algorithms for FTFL with improved ratios.


\bibliographystyle{plain}
\bibliography{facility}
%\printbibliography

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\section{An Elementary Proof of the Expected Connection Cost}


In the $1+2/e=1.736$-approximation, we need to show the following inequality
%
\begin{equation}
  \label{eq:dist}
  d_1 y_1 + d_2 y_2 (1-y_1) + d_3 y_3 (1-y_1)(1-y_2) + \ldots + d_l y_l \Pi_{s=1}^{l-1} (1-y_s) \leq (d_1 y_1 + d_2 y_2 + \ldots + d_l y_l) (1 - \Pi_{s=1}^l (1-y_s))
\end{equation}
%
for $d_1\leq d_2 \leq \ldots \leq d_l$ and $\sum_{s=1}^l y_s = 1, y_s \geq 0$.

In this section we give a new proof of this inequality, much
simpler than the existing proof in
\cite{ChudakS04}~\footnote{It is known that Sviridenko has
  proved a similar lemma using Chebyshev's sum inequality,
  but the cited reference~\cite{Svi02} contains a different
  proof from ours here.}.  We derive this inequality from
the following generalized version of the Chebyshev Sum
Inequality:
%
\begin{equation}
  \label{eq:cheby}
  \sum_{i} p_i \sum_j p_j a_j b_j \leq \sum_i p_i a_i \sum_j p_j b_j,
\end{equation}
%
where each summation below runs from $1$ to $l$ and the sequences 
$(a_i)$, $(b_i)$ and $(p_i)$ satisfy the following conditions:
$p_i\geq 0, a_i \geq 0, b_i \geq 0$ for all $i$, $a_1\leq a_2 \leq
\ldots \leq a_l$, and $b_1 \geq b_2 \geq \ldots \geq b_l$.

Given inequality (\ref{eq:cheby}), we can obtain our inequality
(\ref{eq:dist}) by simple substitution
%
\begin{equation}
  p_i \leftarrow y_i, a_i \leftarrow d_i, b_i \leftarrow
  \Pi_{s=1}^{i-1} (1-y_s)
\end{equation}

For the sake of completeness, we include the proof of inequality (\ref{eq:cheby}), 
due to Hardy, Littlewood and Polya~\cite{HardyLP88}. The idea is to evaluate the 
following sum:
%
\begin{align*}
  S &= \sum_i p_i \sum_j p_j a_j b_j - \sum_i p_i a_i \sum_j p_j b_j
	\\
  & = \sum_i \sum_j p_i p_j a_j b_j - \sum_i \sum_j p_i a_i p_j b_j
	\\
  & = \sum_j \sum_i p_j p_i a_i b_i - \sum_j \sum _i p_j a_j p_i b_i
	\\
	&= \half \cdot \sum_i \sum_j (p_i p_j a_j b_j - p_i a_i p_j b_j + p_j p_i a_i
  							b_i - p_j a_j p_i b_i)
\\
  &= \half \cdot \sum_i \sum_j p_i p_j (a_i - a_j)(b_i - b_j) \leq 0.
\end{align*}
The last inequality holds because $(a_i-a_j)(b_i-b_j) \leq 0$, since the sequences
$(a_i)$ and $(b_i)$ are ordered oppositely.

\end{document}

% marek Tue Jul  3 10:21:05 PDT 2012
% marek Sun Jul  1 14:57:39 PDT 2012
% lyan Sat Jun 30 2012, 22:01:27
% marek Sat Jun 30 10:08:59 PDT 2012
% lyan Fri Jun 29 19:54:18 PDT 2012
% marek Thu Jun 28 09:21:14 PDT 2012
% lyan Thu Jun 28 00:11:28 PDT 2012
% marek Wed Jun 27 11:24:07 PDT 2012
% lyan Wed Jun 27 2012, 10:08:21
% marek Tue Jun 26 14:48:45 PDT 2012
% lyan Mon Jun 25 2012, 22:23:13
% marek Sun Jun 24 16:46:23 PDT 2012
% marek Wed Jun 20 04:42:40 PDT 2012
% lyan, Sun Jun 17 2012, 09:49:22
% marek Sat Apr  7 16:42:21 PDT 2012
% marek Thu Apr  5 11:39:58 PDT 2012
% marek Wed Apr  4 11:28:20 PDT 2012
% lyan, 04/01/12 10:20 PM
% lyan, Mon Mar 26 2012, 09:10:54
% lyan, Tue Mar 20 2012, 23:28:17
% lyan, 03/18/12 12:28 PM
% marek Sat Mar 17 13:42:32 PDT 2012
% marek, Wed Mar  7 21:28:24 PST 2012
% marek Mon Mar 12 12:08:25 PDT 2012
