\section{Introduction}

In the \emph{Fault-Tolerant Facility Placement} problem
(FTFP), we are given a set $\sitesset$ of \emph{sites} at
which facilities can be built, and a set $\clientset$ of
\emph{clients} with some demands that need to be satisfied
by different facilities. A client $j\in\clientset$ has demand
$r_j$. Building one facility at a site $i\in\sitesset$ incurs a cost
$f_i$, and connecting one unit of demand from client $j$ to
a facility at site $i$ costs $d_{ij}$. Throughout the
paper we assume that the connection costs (distances)
$d_{ij}$ form a metric, that is, they are
symmetric and satisfy the triangle inequality. In a feasible solution, some
number of facilities, possibly zero, are opened at each site
$i$, and demands from each client are connected to those
open facilities, with the constraint that demands from the
same client have to be connected to different
facilities. Note that any two facilities at the same site are considered different.

It is easy to see that if all $r_j=1$ then FTFP reduces to
the classic Uncapacitated Facility Location problem (UFL).
If we add a constraint that each site can have at most one
facility built on it, then the problem becomes equivalent to the
Fault-Tolerant Facility Location problem (FTFL). One
implication of the one-facility-per-site restriction in FTFL
is that $\max_{j\in\clientset}r_j \leq |\sitesset|$, while
in FTFP the values of $r_j$'s can be much bigger than
$|\sitesset|$.

The UFL problem has a long history; in particular, great
progress has been achieved in the past two decades in
developing techniques for designing constant-ratio
approximation algorithms for UFL.  Shmoys, Tardos and
Aardal~\cite{ShmoysTA97} proposed an approach based on
LP-rounding, that they used to achieve a ratio of 3.16.
This was then improved by Chudak~\cite{ChudakS04} to 1.736,
and later by Sviridenko~\cite{Svi02} to 1.582.
The best known ``pure" LP-rounding algorithm is due to
Byrka~{\etal}~\cite{ByrkaGS10} with ratio 1.575. 
Byrka and Aardal~\cite{ByrkaA10} gave a hybrid algorithm that combines LP-rounding
and dual-fitting (based on \cite{JainMMSV03}), achieving a ratio of 1.5.  Recently,
Li~\cite{Li11} showed that, with a more refined analysis and
randomizing the scaling parameter used in \cite{ByrkaA10}, the ratio can be improved
to 1.488. This is the best known approximation result for UFL.  
Other techniques include the primal-dual algorithm with ratio 3 by
Jain and Vazirani~\cite{JainV01}, the dual fitting method by
Jain~{\etal}~\cite{JainMMSV03} that gives ratio 1.61, and a
local search heuristic by Arya~{\etal}~\cite{AryaGKMMP04}
with approximation ratio 3.  On the hardness side, UFL is
easily shown to be {\NP}-hard, and it is known that it is
not possible to approximate UFL in polynomial time with
ratio less than $1.463$, provided that
$\NP\not\subseteq\DTIME(n^{O(\log\log
  n)})$~\cite{GuhaK98}. An observation by Sviridenko
strengthened the underlying assumption to $\PP\ne \NP$ (see \cite{vygen05}).

FTFL was first introduced by Jain and
Vazirani~\cite{JainV03} and they adapted their primal-dual
algorithm for UFL to obtain a ratio of
$3\ln(\max_{j\in\clientset}r_j)$.  All subsequently
discovered constant-ratio approximation algorithms use
variations of LP-rounding.  The first such algorithm, by
Guha~{\etal}~\cite{GuhaMM01}, adapted the approach for UFL
from \cite{ShmoysTA97}.  Swamy and Shmoys~\cite{SwamyS08}
improved the ratio to $2.076$ using the idea of pipage
rounding introduced in \cite{Svi02}. Most recently,
Byrka~{\etal}~\cite{ByrkaSS10} improved the ratio to 1.7245
using dependent rounding and laminar clustering.

FTFP is a natural generalization of UFL. It was first
studied by Xu and Shen~\cite{XuS09}, who extended the
dual-fitting algorithm from~\cite{JainMMSV03} to give an
approximation algorithm with a ratio claimed to be
$1.861$. However their algorithm runs in polynomial time
only if $\max_{j\in\clientset} r_j$ is polynomial in
$O(|\sitesset|\cdot |\clientset|)$ and the analysis of the
performance guarantee in \cite{XuS09} is flawed\footnote{Confirmed through
  private communication with the authors.}.  To date, the
best approximation ratio for FTFP in the literature is $4$,
established by Yan and Chrobak~\cite{YanC11}, while the only
known lower bound is the $1.463$ lower bound for UFL
from~\cite{GuhaK98}, as UFL is a special case of FTFP.
If all demand values $r_j$ are equal, the problem can be solved
by simple scaling and applying LP-rounding algorithms for UFL. This does
not affect the approximation ratio, thus achieving ratio $1.575$ for this
special case (see also \cite{LiaoShen11}).

\smallskip

The main result of this paper is an LP-rounding algorithm
for FTFP with approximation ratio 1.575, matching the best
ratio for UFL achieved via the LP-rounding method
\cite{ByrkaGS10} and significantly improving our earlier
bound in~\cite{YanC11}. In Section~\ref{sec: polynomial
  demands} we prove that, for the purpose of LP-based
approximations, the general FTFP problem can be reduced to
the restricted version where all demand values are
polynomial in the number of sites.  This \emph{demand
  reduction} trick itself gives us a ratio of $1.7245$,
since we can then treat an instance of FTFP as an instance
of FTFL, by creating a sufficient (but polynomial) number of
facilities at each site and using the algorithm
from~\cite{ByrkaSS10}.

The reduction to polynomial demands suggests an approach where
clients' demands are split into unit demands. These unit demands can
be thought of as ``unit-demand clients'', and a natural approach would
be to adapt LP-rounding methods from
\cite{gupta08,ChudakS04,ByrkaGS10} to this new set of unit-demand
clients.  Roughly, these algorithms iteratively pick a client that
minimizes a certain cost function (that varies for different
algorithms) and open one facility in the neighborhood of this
client. The remaining clients are then connected to these open
facilities.  In order for this to work, we also need to convert the
optimal fractional solution $(\bfx^\ast,\bfy^\ast)$ of the original
instance into a solution $(\barbfx,\barbfy)$ of the modified instance
which then can be used in the LP-rounding process. This can be thought
of as partitioning the fractional solution, as each connection value
$x^\ast_{ij}$ must be divided between the $r_j$ unit demands
of client $j$ in some way. In Section~\ref{sec: adaptive partitioning} we
formulate a set of properties required for this partitioning to
work. For example, one property guarantees that we can connect demands
to facilities so that two demands from the same client are connected
to different facilities. Then we present our \emph{adaptive
  partitioning} technique that computes a partitioning with all the
desired properties. Using adaptive partitioning we were able to extend
the algorithms for UFL from \cite{gupta08,ChudakS04,ByrkaGS10} to
FTFP. We illustrate the fundamental ideas of our approach in
Section~\ref{sec: 3-approximation}, showing how they can be used to
design an LP-rounding algorithm with ratio $3$.  In Section~\ref{sec:
  1.736-approximation} we refine the algorithm to improve the
approximation ratio to $1+2/e\approx 1.736$.  Finally, in
Section~\ref{sec: 1.575-approximation}, we improve it even further to
$1.575$ -- the main result of this paper.

Summarizing, our contributions are two-fold: One, we show
that the existing LP-rounding algorithms for UFL can be
extended to a much more general problem FTFP, retaining the
approximation ratio. We believe that, should even better
LP-rounding algorithms be developed for UFL in the future,
using our demand reduction and adaptive partitioning
methods, it should be possible to extend them to FTFP.
In fact, some improvement of the ratio
should be achieved by randomizing the scaling parameter
$\gamma$ used in our algorithm, as Li showed in \cite{Li11}
for UFL.  (Since the ratio $1.488$ for UFL in~\cite{Li11}
uses also dual-fitting
algorithms~\cite{MahdianYZ06}, we would not obtain the same
ratio for FTFP yet using only LP-rounding.)

Two, our ratio of $1.575$ is significantly better than the
best currently known ratio of $1.7245$ for the
closely-related FTFL problem. This suggests that in the
fault-tolerant scenario the capability of creating
additional copies of facilities on the existing sites makes
the problem easier from the point of view of approximation.
